Technical Report

### 2024-04-30 Reports/tech_report1.tex

>>>>

\begin{align*}
	comp(c,c') &= \sum_{b} u(b)\min(|W_{bcd}|,|W_{bc'd}|)\\
	comp(c) &= \sum_{c'\in C} comp(c,c')
\end{align*}
Here, $d$ is the fixed target node. $C$ is a specific set. It can be the set of all nodes in that layer (denoted as ALL), or some thing more complex. The one we have tested is the set CURRENT: first pick two (or one) nodes by $comp(c,c')$ into the open node list, then
